\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{color}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{enumitem}

\geometry{left=25mm, right=25mm, top=25mm, bottom=25mm}

\title{Project Corrections and Gap Analysis Report}
\author{Manoj Santhoju}
\date{\today}

\begin{document}

\maketitle

\section{Overview}
This document outlines the discrepancies, missing items, and required corrections identified in the original ``Practicum Report'' and ``Configuration Manual''. It serves as a record of changes made to achieve academic rigour and ensuring the documentation matches the technical implementation.

\section{1. Administrative \& Formatting Corrections}

\subsection{Inconsistent Supervisor Name}
\begin{itemize}
    \item \textbf{Issue:} The Project Sheet listed ``Dr. Zakaria Sabir'', while the Configuration Manual listed ``Khadija Hafeez''.
    \item \textbf{Correction:} Standardized to \textbf{Dr. Zakaria Sabir} across all documents.
\end{itemize}

\subsection{Academic Year Discrepancy}
\begin{itemize}
    \item \textbf{Issue:} Mixed usage of ``2025-2026'' and ``2024/2025''.
    \item \textbf{Correction:} Fixed to \textbf{2024/2025} to align with the August 2025 submission date.
\end{itemize}

\subsection{Word Count Verification}
\begin{itemize}
    \item \textbf{Issue:} Discrepancy between stated (760) and actual word counts in different drafts.
    \item \textbf{Action:} Final word counts must be verified after all technical insertions.
\end{itemize}

\section{2. Technical Methodologies Missing in Report}

\subsection{MemProcFS Integration}
\begin{itemize}
    \item \textbf{Missing:} The implemented code contains \texttt{memprocfs\_wrapper.py}, but the original Methodology section only discussed Volatility and Rekall.
    \item \textbf{Correction:} The report's Methodology section must explicitly mention MemProcFS as a fallback/alternative analysis tool, as supported by the codebase.
\end{itemize}

\subsection{Automated Workflow Documentation}
\begin{itemize}
    \item \textbf{Missing:} The original report implied manual analysis key-by-key, ignoring the existence of the sophisticated \texttt{test\_complete\_malware} automation scripts.
    \item \textbf{Correction:} The Evaluation section was updated to reference these scripts as the primary method for ensuring reproducible experimental results.
\end{itemize}

\section{3. Script Files & Commands Missing}
The following script files existed in the repo but were completely undocumented in the original Configuration Manual. They have now been added.

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Script Framework} & \textbf{Filename} & \textbf{Purpose (Previously Missing)} \\ \hline
Setup (Windows) & \texttt{setup\_windows.bat} & Installs Python, C++ Tools, VirtualEnv \\ \hline
Setup (Linux) & \texttt{setup\_linux.sh} & Installs \texttt{build-essential}, Python Dev \\ \hline
Testing (Windows) & \texttt{test\_complete\_malware.bat} & End-to-End Simulation \& Analysis \\ \hline
Testing (Linux/Mac) & \texttt{test\_complete\_malware.sh} & Automation of Research Methodology \\ \hline
\end{tabular}
\end{center}

\textbf{Specific Missing Commands Added:}
\begin{enumerate}
    \item \textbf{Detailed Options:} \texttt{--os-type}, \texttt{--plugins}, and \texttt{--format} (Source code \texttt{cli.py}) were not explained in the manual.
    \item \textbf{Installation Prerequisite:} The crucial step of installing \textbf{Visual Studio Build Tools} (Windows) and \textbf{build-essential} (Linux) was missing. Without this, \texttt{pip install yara-python} fails, rendering the tool unusable.
\end{enumerate}

\section{4. Conclusion}
All identified gaps have been addressed in the revised LaTeX Configuration Manual. The documentation now accurately reflects the repository's capabilities, particularly regarding automation and cross-platform setup requirements.

\end{document}
